A state space model reveals the rich and varied dynamics of replay

### 2020-07-15 Article.tex
Update on Overleaf.

Using this model, we found that most SWRs contained spatially coherent content. Importantly, this content was not predominantly trajectories that occurred at many times the speed of the animal, but trajectories that were much closer to the animal's actual movement speed. Many of these events did not simply represent the animal's current location, but some other location on track.

Our results challenge the notion that hippocampal replays consist only of high speed events. Are stationary events during SWR that represent the animal's position different from stationary events that represent non-local positions

Our results complement those of Stella and colleagues \cite{StellaHippocampalReactivationRandom2019} who found that hippocampal replay trajectories followed Brownian like diffusion dynamics. We found that  We also clarify how these results can coexist with Pfeiffer and Foster \cite{PfeifferAutoassociativedynamicsgeneration2015} who found that a subset of replay trajectories alternated between stationary and jumpy representations. We find that, for our task, these jumpy representations were relatively rare.

@@

Our model is similar to the competing temporal models approach of Johnson and Redish 2008 \cite{JohnsonMeasuringdistributedproperties2008}, but allows for more . Our model also represents a middle ground between Hidden Markov-style models \cite{MaboudiUncoveringtemporalstructure2018, ChenBayesiannonparametricmethods2016, LindermanBayesiannonparametricapproach2016}, which seek to be environment-agnostic discovers of sequential patterns but require a lot of data, and typical Bayesian decoder, which has very restrictive assumptions about the nature of the trajectories. allows SWR to quickly be identified because of the discrete states. Can work in 2D. Can precisely identify timing of dynamics because of acausal decoding

>>>>

Using this model, we found that most SWRs contained spatially coherent content. Importantly, this content was not predominantly trajectories that occurred at many times the speed of the animal, but trajectories that were much closer to the animal's actual movement speed. Many of these events did not simply represent the animal's current location, but other locations on track.

Our results challenge the notion that hippocampal replays are necessarily many times the speed of the animal. Are stationary events during SWR that represent the animal's position different from stationary events that represent non-local positions

@@

Our results complement those of Stella and colleagues \cite{StellaHippocampalReactivationRandom2019} who found that hippocampal replay trajectories followed Brownian-like diffusion dynamics. We found that  We also clarify how these results can coexist with Pfeiffer and Foster \cite{PfeifferAutoassociativedynamicsgeneration2015} who found that a subset of replay trajectories alternated between stationary and jumpy representations. We also found a log normal distribution of speeds, but it should be noted that they presented their results in terms of  at least for our task, these jumpy representations are relatively rare.

Our model is similar to the competing temporal models approach of Johnson and Redish 2008 \cite{JohnsonMeasuringdistributedproperties2008}, but allows for more . Our model also represents a middle ground between Hidden Markov-style models \cite{MaboudiUncoveringtemporalstructure2018, ChenBayesiannonparametricmethods2016, LindermanBayesiannonparametricapproach2016, ChenUncoveringspatialtopology2012}, which seek to be environment-agnostic discovers of sequential patterns but require a lot of data, and typical Bayesian decoder, which has very restrictive assumptions about the nature of the trajectories. allows SWR to quickly be identified because of the discrete states. Can work in 2D. Can precisely identify timing of dynamics because of acausal decoding
